\documentclass[12pt]{article}

\title{High Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors}
\author{Thomas, Robert, etc.}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We demonstrate that high resolution time of flight mass spectrometry can be successfully applied to detect gas-phase product in heterogeneous catalysis. Combining the instrument with the highly sensitive microreactors opens the possibility to measure on system that are otherwise difficult due to ....
\end{abstract}

\section{Introduction}
Something about the relevance of this system. Catalysis is interesting because... Typical problems with QMS approach. 

\section{System design}
The system consists of a TOF, microreactor and gas handling. Complete system suitable for measurements of small amounts of catalyst with high sensitivity.

\subsection{Microreactor and gas handling}

\subsubsection{Gas handling}
Something about the gas inlet...

\subsubsection{The microreactor platform}
A microreactor platform is used for testing catalyst with high sensitivity. The microreactor is fabricated in silicon and measures 20x15 mm. The reactor consists of two gas inlets, an outlet, a reactor volume and a capillary used for probing the gas from the reactor volume. The reactor volume is 3 $\mu$m deep and 1 cm in diameter resulting in a 240 nL volume. The two gas inlets are combined on the chip where the gases mix by diffusion. The capillary is designed such that approximately $10^{15}$ molecules/s is probed from the reactor volume. Any surplus of gas from the two inlets that does not enter the reactor volume is directed through the outlet into a turbo pump. The design ensures that all molecules entering the reactor volume hence exposed to the catalyst under investigation is detected giving the system high sensitivity.   

\subsection{Time of flight}

\subsubsection{Ionization of gas}

\section{Test system}
Ammonia oxidation

\section{Summary}

\section{Acknowledgements}

\end{document}
